%======================================= Agradecimentos =======================================
\chapter*{Acknowledgment}

%\noindent Text \\[2mm]

\noindent More than two years were necessary to finish this work and many people got involved. \\

First of all, I would like to thank Prof. Dr. Jos\'e Mario De Martino for his guidance, incentive, friendship and patience in this journey. \\

Many thanks to Dr. S\'ebastien Marcel, Dr. Andr\'e Anjos and Ivana Chingovska, from the IDIAP Research Institute. Their supervision in the four months in Switzerland were definitely decisive to complete this masters dissertation. A special thanks to Dr. Andr\'e Anjos for his guidance, friendship and the doses of cacha\c{c}a. I also would like to thank Dr. Manuel G{\"u}nter, Dr. Elie El Khoury, Dr. Nesli Erdogmus, Laurent El Shafey and Jukka Komulainen (University of Oulu) for their support and fellowship. \\

Thanks to CPqD, for encourage me in this project, releasing so many hours of work and for fund part of this research. A special thanks to Norberto Alves Ferreira, Claudinei Martins, Eliana De Martino, Emilio Nakamura, Marcus de Assis Angeloni, Jos\'e Eduardo de Carvalho Silva, Ricardo Violatto, Mario Uliani and the big master Flavio Sim\~oes. \\

Thanks to my friends Geovane Shimizu, Bruno Cafeo and Diego Silva for just being there. \\

Thanks to my parents Antonio Alberto (Tote) and Sueli, and brother Rodrigo for the unconditional love and support, even don't understanding a bit what I am doing. A special thanks to my grandma Christina. She was a great example of a teacher and also my first one. \\

A very special thanks to my best friend and fianc\'ee Carolina Scarton, for her support, care, patience and unconditional love during all these years.


\newpage %verso em branco

\null

%==============================================================================================
